TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
minor

In Definition~\ref{def:prod}, we judge if a tactic is productive from its
contribution to the search tree.

\begin{definition}\label{def:prod} (Productive tactic)
The application of a tactic on an open goal is called productive if and only if
all the following conditions are satisfied:
\begin{itemize}
\item It does not fail or timeout. To prevent tactics from looping, we
interrupt tactics after a short amount of time (0.05 seconds).
\item It does not loop, i.e. its output does not contain any goals that appears
in the ancestor of the node of the current goal.
\item It is not a parallel step, i.e. its output is not a superset
of a list of goals produced from the same goal.
\end{itemize}

@@

\paragraph{Resolution}
The search ends when the algorithm reaches one of these 3 conditions:
\begin{itemize}
\item It finds a proof, i.e. the root node is solved. In this case,
the search returns a minimized and
prettified proof script (see Section~\ref{sec:proofdisplay}).
\item It saturates, i.e. there is no tactics to be applied to any open goal.
This happens less than 10 times in the full-scale experiment.
\item It exceeds a given time limit set by default to 60 seconds.
\end{itemize}

@@

The first idea is to select tactic-goal pairs and theorems by their similarity
with $c$ (i.e $\mathit{Predictions}^{\mathit{tactic}}_{500} (c)$ and
$\mathit{Predictions}^{\mathit{theorem}}_{500} (c)$).
However, this selection may not be adapted to later stages of
the proof where goals may have drifted significantly from $c$. In order to
anticipate the production of diverse goals, our prediction during preselection
takes dependencies between objects of the same dataset into account.
This dependency relation is assymetric. Through the relation, each object has
multiple children and at most one parent.
Once a dependency relation is established we can calculate a dependency score
for each object, which is the maximum of its similarity score
and the similarity score of its parent. In the end, the 500 entries with
highest dependency score are preselected in each dataset.

>>>>

In Definition~\ref{def:prod}, we decide if a tactic is productive based on its
contribution to the search tree.

\begin{definition}\label{def:prod} (productive tactic)
The application of a tactic on an open goal is called productive if and only if
all the following conditions are satisfied:
\begin{itemize}
\item It does not fail or timeout. To prevent tactics from looping, we
interrupt tactics after a short amount of time (0.05 seconds).
\item It does not loop, i.e., its output does not contain any goals that appear
in the ancestor of the node of the current goal.
\item It is not a parallel step, i.e., its output is not a superset
of a list of goals produced from the same goal.
\end{itemize}

@@

\paragraph{Resolution}
The search ends when the algorithm reaches one of these 3 conditions:
\begin{itemize}
\item It finds a proof, i.e., the root node is solved. In this case,
the search returns a minimized and
prettified proof script (see Section~\ref{sec:proofdisplay}).
\item It saturates, i.e., there is no tactics to be applied to any open goal.
This happens less than 10 times in the full-scale experiment.
\item It exceeds a given time limit set by default to 60 seconds.
\end{itemize}

@@

The first idea is to select tactic-goal pairs and theorems by their similarity
with $c$ (i.e. $\mathit{Predictions}^{\mathit{tactic}}_{500} (c)$ and
$\mathit{Predictions}^{\mathit{theorem}}_{500} (c)$).
However, this selection may not be adapted to later stages of
the proof where goals may have drifted significantly from $c$. In order to
anticipate the production of diverse goals, our prediction during preselection
takes dependencies between objects of the same dataset into account.
This dependency relation is assymetric. Through the relation, each object has
multiple children and at most one parent.
Once a dependency relation is established we can calculate a dependency score
for each object, which is the maximum of its similarity score
and the similarity score of its parent. In the end, the 500 entries with
highest dependency score are preselected in each dataset.
